---
title: "boostrapping"
author: "Lizbeth Gomez"
date: "11/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

class slides  [here](https://p8105.com/bootstrapping.html)

repeated sampling framework ina computer - never irl
Bootstraping takes a dataframe you have
not the same anaylisis onthe same data- the dartaset changes a bit 
Iterative process

lets bootstrap!

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)

```

```{r}
set.seed(1)
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 
```


first two models
```{r}
sim_df_const %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy() 
  
sim_df_nonconst %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy() 
```

how can i bootstrap 
writw a function to draw a bootstrap sample based on the dataframe

```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

```{r}
boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) 
```

organize the dattaset
```{r}
boot_straps = 
  data_frame(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )
```

Do some kind of analysis 
```{r}

bootstrap_results =
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x)), 
    results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results)
```

```{r}
bootstrap_results %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))  ##Every time you dra bst sample, now I care about the spread/ distribution (like a se FROM YOUR ESTIMATE?)
```

## try the modelr pckg

```{r, eval=FALSE}

boot_straps =
  sim_df_nonconst %>% 
  modelr::bootstrap(1000) %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x)), 
    results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results) %>% 
group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

